

{During the course of this term project, numerous issues were observed. Some common issues detected during the compilation of the program included various syntax errors and bugs. This encompassed logical issues present during the compilation of code. A never ending loop was most commonly found during multiple reruns, needing constant correction and adjustment. Another issue that arose was ‘under defined array storage usage’ due to having logic statements in unbreakable loops.}

{Addressing these matters in turn brought forth new concerns within the code; stack, time and buffer overflow errors. Albeit being difficult to address these issues, rewriting of the code and recompilation proved to eliminate said problems.  As a result a new code was generated following the pre-identified parameters. This however proved to be a lengthy process despite peer contribution, as the script required constant debugging. }

{For future projects regarding CSV files, it would seem that generating a better algorithm to parse the CSV file on run time would address frequent issues; stack, time and buffer overflow issues. Primarily this form of change would affect time overflow issues, considerably reducing processing time with the preset parameters.}

{Other improvements if this project was to be redone include minimizing the use of additional global variables. This would minimize both stack overflow and buffer overflow issues observed in our code. In addition to reducing global variables, reducing pointer variables dereferencing to null will allow the program to abstain from crashes and exits. Additional improvements for future projects can include adding failsafe mechanisms to highlight errors within the code with great ease.}

{}

{}

{}

{}

{}

{}

{}


